\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-03-22 presentations/cambridge-18-03-2019/presentation.tex
[Presentation] Update CHERI and StkTokens comparison
[Presentation] Edit a few things, Cambridge 19

      \draw node[right=0cm of sp1] { stack pointer };
%      \draw[capa] (r1) edge[->,postaction={decorate},bend left] (sp1);
    \end{onlyenv}

@@

    % Callee stores stack pointer
    \begin{onlyenv}<.->
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (8,5) -- (8,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (16,15) node {heap memory};
    \end{onlyenv}

@@

\begin{frame}
  \frametitle{Proof sketch for a realistic secure compiler}
  \begin{center}
  \begin{tikzpicture}[scale=.5, every node={scale=.5},distance=1cm]
    % \draw<1-6> (-5,0) node {};
    % \draw (5,0) node {};
    % \draw (0,-14) node {};
    \draw<1-> node[draw=black,rounded corners,above] (source) {High-level language};
    \draw<1-> node[draw=black,rounded corners,below=of source] (mca) {Machine code w/ many abstractions};
    \draw<1-> node[draw=black,rounded corners,below=1cm of mca] (mcir) {...};
    \draw<1-> node[draw=black,rounded corners,below=1cm of mcir] (mcs) {Machine code w/ built-in stack};
    \draw<1-> node[draw=black,rounded corners,below=of mcs] (target) {Machine code};

@@

\begin{frame}
  \frametitle{Full abstraction}
  \begin{theorem}[Full abstraction]
  For \tikz[remember picture] \node[inner sep=0pt, outer sep=0pt] (rea) {reasonable};, \tikz[remember picture] \node[inner sep=0pt, outer sep=0pt] (wf) {well-formed};\ $\comp_1$ and $\comp_2$, we have
  \begin{gather*}
    \src{\comp_1} \sconeq \src{\comp_2} \quad \Leftrightarrow \quad    \src{\comp_1} \tconeq \src{\comp_2} \qedhere
  \end{gather*}
\end{theorem}
\vspace{-0.5cm}
\rule{1\textwidth}{0.4pt}
\begin{columns}
  \begin{column}{0.5\textwidth}
    \begin{itemize}[<3->]
    \item \stktokens{} reasonable use of return seals
      \begin{itemize}
      \item Return seals are only used to seal old program pointers.
      \item Every return seal is only used for one call site.
      \item Return seals are not leaked.
      \end{itemize}
    \item<4-> No measures against us
  \end{itemize}
  \end{column}
  \begin{column}{0.5\textwidth}
    \begin{itemize}[<6->]
    \item Component structure.
    \item Sane linker behaviour.
    \end{itemize}
  \end{column}
\end{columns}
\vspace{0.5cm}
\onslide<7>{\centering Should be handled in earlier compiler phase}
\begin{tikzpicture}[remember picture, overlay]
  \draw<2-4> node[rectangle, fit=(rea), draw=myred, rounded corners, inner sep=2pt, yshift=-1pt, xshift=0.75pt] (n1) {};
  \draw<5> node[rectangle, fit=(wf), draw=myred, rounded corners, inner sep=2pt, yshift=-1pt, xshift=0.75pt] (n1) {};
\end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{Conclusion}
\begin{itemize}
\item \stktokens{} ensures well-bracketed control flow and local-state encapsulation.
\item Overlay semantics used to define well-bracketed calls and local state encapsulation.
\item Capability machines may be a good target for secure compilation.
\end{itemize}
  % \begin{description}
  % \item[Formalization of CHERI-like capability machine with linear capabilities]
  % \item[\stktokens{}] a calling convention that provably guarantees LSE and well-bracketed control-flow WBCF
  % \item[Fully-abstract overlay semantics] a novel way to prove LSE and WBCF claims
  %   \begin{itemize}
  %   \item Proven with cross-language logical relations
  %   \end{itemize}
  %   % TODO Mention the proof and logical relation, move to end?
  % \end{description}
\end{frame}

@@

\begin{frame}
  \frametitle{\stktokens{} vs. CHERI stack}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \textbf{\stktokens{}}
      \begin{itemize}
      \item No built-in stack
      \item Fine granularity of security domains
      \item No context switch on call
      \item Caller has the full responsibility for securing call
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \textbf{CHERI stack}
      \begin{itemize}
      \item Central, built-in stack
      \item Call and return instructions interact with stack
      \item Context switch on call/return
      \item Local capabilities cannot cross security boundary
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}
\end{document}

>>>>

      \draw node[right=0cm of sp1] { stack pointer };
      \draw[capa] (r1) edge[->,postaction={decorate},bend left] (sp1);
    \end{onlyenv}

@@

    % Callee stores stack pointer
    \begin{onlyenv}<.->
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (8,5) -- (8,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (16,15) node {heap memory};
      \node at (r1) {0};
    \end{onlyenv}

@@

\begin{frame}
  \frametitle{Proof sketch for a realistic secure compiler}
  \begin{center}
  \begin{tikzpicture}[scale=.5, every node={scale=.5},distance=1cm]
    % \draw<1-6> (-5,0) node {};
    % \draw (5,0) node {};
    % \draw (0,-14) node {};
    \draw<1-> node[draw=black,rounded corners,above] (source) {High-level language};
    \draw<1-> node[draw=black,rounded corners,below=of source] (mca) {Assembly w/ many abstractions};
    \draw<1-> node[draw=black,rounded corners,below=1cm of mca] (mcir) {...};
    \draw<1-> node[draw=black,rounded corners,below=1cm of mcir] (mcs) {Assembly w/ built-in stack};
    \draw<1-> node[draw=black,rounded corners,below=of mcs] (target) {Assembly};

@@

\begin{frame}
  \frametitle{Full abstraction}
  \begin{theorem}[Full abstraction]
  For \tikz[remember picture] \node[inner sep=0pt, outer sep=0pt] (rea) {reasonable};, \tikz[remember picture] \node[inner sep=0pt, outer sep=0pt] (wf) {well-formed};\ $\comp_1$ and $\comp_2$, we have
  \begin{gather*}
    \src{\comp_1} \sconeq \src{\comp_2} \quad \Leftrightarrow \quad    \src{\comp_1} \tconeq \src{\comp_2} \qedhere
  \end{gather*}
\end{theorem}
\vspace{-0.5cm}
\rule{1\textwidth}{0.4pt}
\begin{columns}
  \begin{column}{0.5\textwidth}
    \begin{itemize}[<3->]
    \item \stktokens{} reasonable use of return seals
      \begin{itemize}
      \item Return seals are only used to seal old program pointers.
      \item Every return seal is only used for one call site.
      \item Return seals are not leaked.
      \end{itemize}
    \item<4-> No measures against us
  \end{itemize}
  \end{column}
  \begin{column}{0.5\textwidth}
    \begin{itemize}[<6->]
    \item Component structure
    \item Sane linker behaviour
    \end{itemize}
  \end{column}
\end{columns}
\vspace{0.5cm}
\onslide<7>{\centering Should be handled in earlier compiler phase}
\begin{tikzpicture}[remember picture, overlay]
  \draw<2-4> node[rectangle, fit=(rea), draw=myred, rounded corners, inner sep=2pt, yshift=-1pt, xshift=0.75pt] (n1) {};
  \draw<5-6> node[rectangle, fit=(wf), draw=myred, rounded corners, inner sep=2pt, yshift=-1pt, xshift=0.75pt] (n1) {};
\end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{Conclusion}
\begin{itemize}
\item \stktokens{} ensures well-bracketed control flow and local-state encapsulation.
\item Overlay semantics used to define well-bracketed calls and local-state encapsulation.
\item Capability machines may be a good target for secure compilation.
\end{itemize}
  % \begin{description}
  % \item[Formalization of CHERI-like capability machine with linear capabilities]
  % \item[\stktokens{}] a calling convention that provably guarantees LSE and well-bracketed control-flow WBCF
  % \item[Fully-abstract overlay semantics] a novel way to prove LSE and WBCF claims
  %   \begin{itemize}
  %   \item Proven with cross-language logical relations
  %   \end{itemize}
  %   % TODO Mention the proof and logical relation, move to end?
  % \end{description}
\end{frame}

@@

\begin{frame}
  \frametitle{\stktokens{} vs. CHERI stack}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \textbf{\stktokens{}}
      \begin{itemize}
      \item Single stack
      \item Fine granularity of security domains
      \item No context switch on call
      \item Caller has the full responsibility for securing call
      \item Supports higher-order functions
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \textbf{CHERI stack}
      \begin{itemize}
      \item Per component stack and trusted centrally-managed stack
      \item Call and return instructions interact with stack
      \item Context switch on call/return
      \item Local capabilities cannot cross security boundary
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}
\end{document}
